### 2024-01-15 documentation/thesis/thesis_document.tex
more thesis

\hypertarget{charakterisation-of-permanent-magnets}{%
\subsection{Charakterisation of Permanent
Magnets}\label{charakterisation-of-permanent-magnets}}

The shimming process described describes how, after the field magnet has
been set up, if the homogeneous magnetic flux densities are not
sufficient, these can be adjusted manually by means of adjustments to
the setup or, if the hardware allows it, by software. In addition, the
causes that cause the inhomogeneity, the output permanent magnet, are
also known.

As a result, there is the possibility of using the shimming process or
checking the permanent magnets used in advance before they are used in a
Hallbach configuration.

@@

\cite{Wickenbrock_2021}

@@

The application of the developed framework for the characterization of
different magnets and the integration of magnetic field sensors serve as
practical applications and validation of the developed solution.

>>>>

The shimming process described describes how, after the field magnet has
been set up, if the homogeneous magnetic flux densities are not
sufficient, these can be adjusted manually by means of adjustments to
the setup or, if the hardware allows it, by software. In addition, the
causes that cause the inhomogeneity, the output permanent magnet, are
also known. As a result, there is the possibility of using the shimming
process or checking the permanent magnets used in advance before they
are used in a Hallbach configuration.

In order to measure the magnets individually, there are already
implementations that use different measurement methods to determine the
field strength of individual magnets. Individual measuring points are
recorded. This data is then evaluated in separate software
\cite{Wickenbrock_2021}.

@@

This form of data processing of previously characterized magnetic data
is currently being implemented experimentally in projects using various
algorithms \cite{Wickenbrock_2021}. Standard sorting algorithms are
used as well as specialized algorithms for optimizing homogeneity by
rotating the individual magnets in a Hallbach ring relative to each
other \cite{HalbachMRIDesigner}.

These are each separate projects that implement individual aspects of
data processing, which realize the process of measuring individual
magnets by manual combination. However, there are still compatibility
problems and limitations in the adaptation of hardware and software.

Special algorithms from various projects are used to optimize
homogeneity. The challenge here is to ensure the seamless integration
and compatibility of these algorithms into the overall process. This
should make it possible to create a workflow from the individual magnet
to the finished optimized \gls{cad} model of a halbach ring.

@@

The application of the developed framework for the characterization of
different magnets and the integration of various available magnetic
field sensors serve the practical application and validation of the
developed solution.
